\documentclass{article} % Use the custom invoice class (invoice.cls)
\usepackage{todonotes}
\setuptodonotes{inline}

\title{dUSD Test Plan}
\begin{document}


\maketitle


\section{Interactions}

\subsection{Price oracle}

\todo{What will the price oracle store? Suggestion: The last 48h of data. \\
The reason to store more than only the most recent price, is such that the OSM
can be used to determine how long a vault has been in a disastrous state (i.e.
collateralization ratio smaller than $1$), which is useful to determine when to
bind the vault to the buffer and mint dUSD in order to pay back the debt.}

A price oracle is a timeline of UTXOs\footnote{
  In the blockchain industry, people often talk about concepts like price
  oracles and DEX pools. However, within the EUTXO system built by Cardano, the
  fundamental concept we are dealing is the UTXO. This means that we are dealing
  with a `state' of a price oracle as the fundamental concept, not the price
  oracle itself. Now, Plutus scripts like price oracles, between being created
  and destroyed, basically only allow to be updated and read. This means that
  one can draw a `timeline' through a series of UTXO, each one disappearing into
  a transaction that produces the next. This set of UTXOs is what is referred to
  as ``the price oracle''.
}
which stores the price of a given asset (e.g. ADA) in terms of a reference
currency (USD). \\

A number of price oracles will be created for each asset of interest.
The person creating each price oracle will connect it to a price feed coming
from some CEX/DEX. \\

Next, an Oracle Security Module (OSM) will be implemented.
This is another ``timeline of UTXOs'', which allows admin to select a number of
price oracles as trusted price feeds and combines their prices in a secure way.
The resulting price is exposed to the blockchain ecosystem.

\subsubsection{Read}

The OSM can read all the pricing data stored in the price oracle.

\subsubsection{Write}

The owner/creator of the price oracle can write a new price value to the oracle.

\subsection{Oracle security module}

\subsubsection{Read the `current' price}

\todo{How current do we want the price to be? \\
MakerDAO puts a $1$ hour delay here, to avoid the price oracles from messing
with the system for arbitrage purposes. The problem with that approach is that
it requires governance to react within $1$ hour, and that it endangers vault
liquidation by not making it interesting for liquidators to liquidate a vault
quickly enough. \\
Alternatively, we could build in robustness against some price oracle owners
trying to hack the system by allowing the OSM to shut down the system if the
values different price oracles proclaim, are too widely spread. \\
If we want there to be a time delay in the OSM price, we have to implement an
extra interaction allowing admin to update this value.}

Transactions in the dUSD protocol will read the `current' price of ADA relative
to USD from the OSM.

\todo{Should the OSM shut down the protocol if it has not been updated for too
long?}

\subsubsection{Update}

Anyone can create a transaction to connect the OSM to all of the price oracles
it currently accepts, and update its own datum based on their information.
This is to be rewarded (a little).

\subsubsection{Update list of accepted price oracles}

Admin/governance can update the list of price oracles accepted by the OSM.

\todo{Should the OSM (temporarily) unaccept a price oracle if its price has not
been updated for too long?}

\subsection{Any User}

\subsubsection{Collect information on the user's vaults}

As a user, I want to be able to collect information on my vaults. By "my
vaults", we mean the vaults created by the user. They can only be used by that
user (except for the liquidation procedure, see below).

\subsubsection{Initialize vault}

As a user, I want to be able to open a new vault.

\subsubsection{Deposit}

As a user, I want to be able to deposit ADA into a vault, so that I may take out
a loan of dUSD (see below).

\subsubsection{Withdrawal}

As a user, I want to be able to withdraw ADA from a vault.

\subsubsection{Take out loan}

As a user, I want to be able to take out a loan in dUSD against the collateral I
put into one of my vaults.

\subsubsection{Pay back loan}

As a user, I want to be able to pay back (part of) a loan in dUSD I created in
one of my vaults. In doing so, I am paying a stability fee to the buffer.

\subsubsection{Liquidate someone else's vault}

...

\subsection{Admin}

\subsubsection{Trigger surplus auction (sick vault)}

\subsubsection{Trigger surplus auction (buy back dana)}

\subsubsection{Trigger debt auction}

\subsubsection{Set liquidation fee}

\subsubsection{Set liquidation ratio}

\subsubsection{Set stability fee}

\subsubsection{Set debt floor}

\subsubsection{Set debt ceiling}

\section{Acceptance criteria}

\subsection{Price oracle}

\begin{itemize}
  \item Only the owner can write to the oracle
  \item Anyone can read the price data
  \item Writing a price values removes outdated price values (older than 48
    hours) from the datum.
\end{itemize}

\subsection{Oracle security module}

\begin{itemize}
  \item Admin (and only admin) can update the list of accepted price oracles
  \item The OSM's price information cannot be updated without linking to all
    accepted price oracles
  \item The price oracles are read-only inputs to the ``update OSM'' endpoint
  \item Reading the current price after updating the OSM's price information and
    waiting for the given time delay, leads to the predicted `current' price
    \todo{What is the current price given the list of price oracles? The
    median?}
\end{itemize}

\subsection{Vaults}

Each user should have access to a website at "www.ardana-vaults.com". This
website must be able to connect to their wallet to find out who they are and
allow them to set up vaults and interact with their existing vaults. \\

Decisions to be made:
\begin{itemize}
  \item Do we want the interface to be a website or an app?
  \item Which domain name will the website live at?
\end{itemize}

\subsubsection{Collect information on the user's vaults}

The vault website looks up the requested information and displays it in an
aesthetic and clear overview. \\

Requested information: How many vaults does the user have, how much collateral
and debt do they each have, what are their collateralization ratios, how
dangerous is it to have that collateralization ratio? \\

Decisions to be made:
\begin{itemize}
  \item Is the list of requested information correct? Anything to be added,
    removed or updated?
\end{itemize}

\subsubsection{Initialize}

The vault website should have a button to open a new vault.

\subsubsection{Deposit}

The vault website has a form that allows each user to pick one of their vaults
and deposit ADA into it. \\

Restrictions:
\begin{itemize}
  \item You have at least the amount of ADA in your wallet that you would like
    to deposit.
\end{itemize}

Decisions to be made:
\begin{itemize}
  \item Do we want to implement a maximum amount of collateral? MakerDAO has
    this, not sure why.
  \item Do we want to implement a mininum amount of collateral? If so, is this
    in total per vault, or per deposit?
\end{itemize}

Questions:
\begin{itemize}
  \item How will we figure out from which UTXO in your wallet to take the ADA?
\end{itemize}

\subsubsection{Withdrawal}

The vault website has a form that allows each user to pick one of their vaults
and withdraw ADA from it. \\

Restrictions:
\begin{itemize}
  \item Withdrawing this amount of ADA from that vault doesn't sink its
    collateralization ratio below the liquidation ratio.
\end{itemize}

\subsubsection{Take out loan}

The vault website has a form that allows a user to pick one of their vaults and
take out a dUSD loan in it, against his collateral. \\

Restrictions:
\begin{itemize}
  \item If the total amount of debt in the vault before taking out the loan is 0,
    the amount of the loan must be greater than or equal to the debt floor for the
    vault's collateral type.
  \item The total amount of debt in the vault after taking out the loan is less than or
    equal to the debt ceiling for the vault's collateral type.
  \item The collateralization ratio in the vault after taking out the loan is greater than
    or equal to the liquidation ratio for the vault's collateral type.
\end{itemize}

\subsubsection{Pay back loan}

The vault website has a form that allows a user to pick one of their vaults and
pack back a (part of a) dUSD loan in it. \\

Restrictions:
\begin{itemize}
  \item The amount of dUSD paid back by the user is less than or equal to the
    amount of dUSD debt in the vault.
  \item The stability fee for the part of loan that is paid back, is sent to the
    buffer as community profit
\end{itemize}

\subsubsection{Liquidate someone else's vault}

...

\subsection{Admin}

\subsubsection{Trigger surplus auction (sick vault)}

\subsubsection{Trigger surplus auction (buy back dana)}

\subsubsection{Trigger debt auction}

\subsubsection{Set liquidation fee}

\subsubsection{Set liquidation ratio}

\subsubsection{Set stability fee}

\subsubsection{Set debt floor}

\subsubsection{Set debt ceiling}

\subsubsection{Set list of price oracles to consider in OSM}

\subsubsection{Set the time interval the OSM waits before using a price update}


\section{Implementation details}

% What do we need in order to make this happen?

\subsection{Price oracle}

Each price oracle will carry an NFT used as a unique identifier.
In addition, each price oracle contains the public hash key of the wallet which
created it, so as to only allow the creator to update the oracle.

\subsection{Oracle security module}

\subsection{Admin}

In order for the admin to add and configure supported collateral types for vaults,
we need an appropriate data structure. We could accomplish this with a map keyed by
collatoral type token name pointing to a record of params containing liquidation ratio,
debt ceiling, debt floor, liquidation fee, stability fee, and any other params to control
incentives for vault participation per that collateral type.


\section{Tests}


% \section{Remarks}
% 
% - Test for Cardano network congestion
% - Test what happens if someone hacks one or more price oracles
% - Other attack vectors which are not specific to our application, should be
%   listed and tested for


\end{document}
